\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{multicol}


\usepackage[left= 0.8in, right = 0.8in, bottom=1in, top=0.6in]{geometry}
\usepackage[svgnames]{xcolor}

\usepackage[bottom]{footmisc}
\textheight=10in
\pagestyle{empty}
\raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME
\newcommand*{\greysquare}{\textcolor{gray}{\blacksquare}}

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}

\newcommand{\header}[1]{{\vspace*{8pt}\hspace*{-16pt} \textsc{\textbf{\large{#1}}}} \vspace*{4pt} \lineunder \vspace*{4pt}}

\newcommand{\experience}[4]{{\vspace{-2pt}\bf{\underline{#1}}} \hfill  #2\\{\textsc{#3} \hfill \emph{#4}\\  }}

\newcommand{\project}[1]{\vspace{-2pt}\underline{\bf{#1}}\vspace{5pt}}

\newcommand{\skilltype}[1]{{\large \underline{#1}} \vspace{3pt} \\}

\newcommand{\skilllevel}[1]{
	\textsc{#1} \\ \vspace*{2pt}
	}

\newcommand{\languageskill}[1]{
    \hspace*{10pt} \textbf{#1}
    }

\newenvironment{skilllist}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newenvironment{subskilllist}{\begin{list}{-}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}

\newcommand{\contact}[5]{
\begin{multicols}{2}
    \raggedcolumns
    \begin{flushleft}
    { \Huge \scshape {#1}}\\
    \end{flushleft}
    
\columnbreak

    \begin{flushright}
    #2 \\ #3 \\
    #4 \\ #5 \\
    \end{flushright}

\end{multicols}

}


\newcommand{\school}[4]{
 \textbf{\underline{#1}} (#3)
 \\ \vspace{3pt} \textsc{#2} 
 \\   #4
\vspace{5pt}
}

\newcommand{\schooltwo}[6]{
    \textbf{\underline{#1}} (#3) 
    \\ \vspace{3pt} \textsc{#2, BS} 
    \\ Minors: \textsc{#5}
    \\  #4 $\bullet$ \textbf{#6}
    \vspace{3pt}
}

\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}


% END RESUME DEFINITIONS

\begin{document}

\small

\contact{Aviva Bulow}{\text{aviva.bulow@gmail.com}}{+1(720)473-3836}{github.com/aviva-bulow}{linkedin.com/in/aviva-bulow}

\vspace{-10pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Professional Summary 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Professional Summary}
A software engineer with 6 years experience (primarily back-end systems in Python), I'm currently learning front-end development (in JavaScript/HTML with React+Bootstrap).

As an analytical thinker with a background in mathematics, I enjoy tackling difficult problems and exploring new ideas. What's more, I'm highly effective at communicating complex concepts across knowledge barriers. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Skills Section
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Skills}
\vspace{-12pt}
\begin{multicols}{4}
\raggedcolumns
    
    \skilltype{Computing}
    \vspace{2pt}
    \skilllevel{Languages: Expert}
        \languageskill{Python}
            \begin{subskilllist}
            \item multiprocessing
            \item unittest
            \item vpython
            \item numpy
            \item Spacy 
            \end{subskilllist}
        
        \skilllevel{General Computing}
        
        \begin{skilllist}
            \item Object Oriented Design
            \item Unit Testing
            \item Complexity Analysis
            \item Parallel Computing
            \item Learning Languages
        \end{skilllist}
            

    
        \columnbreak
    
    \skilltype{Computing}
    \vspace{2pt}
    \skilllevel{Languages: Intermediate}
        \languageskill{Dart} 
            \begin{subskilllist}
            \item Flutter
            \end{subskilllist}
        \languageskill{C}
            \begin{subskilllist}
            \item MPI
            \item OpenMP
            \end{subskilllist}
        
        \languageskill{Java}
            \begin{subskilllist}
            \item awt
            \item swing
            \end{subskilllist}
        \languageskill{R}
            \begin{subskilllist}
                \item ggplot2
            \end{subskilllist}
        \languageskill{SQLite}
        
        
        
        
        \vspace{7pt}
    \columnbreak
        
    \skilltype{Mathematics}
        \begin{skilllist}
            \item Probability and Statistics
            \item Algorithm Analysis
            \item Graph Theory
            \item Proof Construction and Validation
        \end{skilllist}
        
        
    
    \skilltype{Science}
        \begin{skilllist}
        \item Experiment Design
        \item Data Interpretation
        \item Computational Modeling
        \item Data Visualization
        
        \end{skilllist}
        
    \columnbreak

    \skilltype{Leadership}
    
        \begin{skilllist}
            \item Communication
            \item Management (small groups of people/projects)
            \item Organization
            \item Innovation $\&$ Design
        \end{skilllist}
        
        \vspace{2pt}
    
    
\end{multicols}

\vspace{-14pt}

%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%

\header{Experience}

\experience{Software Developer and Founder}{2019 - Present}{SaltSlate \textnormal{(a stealth stage startup)}}{}
\begin{achievements}
	\item Developed a recipe mutation engine that enables scaling, detailed analysis, and efficient scheduling of the user's time.
	
	\item Built an importer that utilizes natural language processing to correctly extract and extrapolate information. It also interfaces with external databases to find nutrition information that it associates with the imported data. 
	
	\item Tools used: \textbf{Python}, \textbf{SQLite}, and \textbf{Spacy} (a natural language toolkit)
	\item Current size: \textbf{18k} lines of code, including 6.5k lines of tests. \textbf{74\%} code coverage.
	
	\end{achievements}


\experience{Graduate Researcher}{2017 - 2019}{UC Berkeley}{Advisor: Thomas Courtade}
\begin{achievements}
	\item Created software to estimate the quality of biosensors.
	\item Utilized diffusion equations, novel differential equations, and Monte Carlo methods.
	
    \item Tools used: \textbf{Python} with modules ``multiprocessing" and ``vpython" (for parallelization, 3D vector calculations, and visualization) and \textbf{R} (for data analysis).
\end{achievements}

\experience{Rotating Graduate Researcher}{2016 - 2017}{UC Berkeley}{Advisors: Rasmus Neilson, Ian Holmes}
\begin{achievements}

	\item Designed and implemented a simulation to test assumptions about data generation. 
	\item Created a stochastic context free grammar. Built a parser for the grammar. \item Tools used: \textbf{R} with ``ggplot2" library (for data visualization) and \textbf{Python}. 
	
	
\end{achievements}

    
\experience{Software Developer and Researcher}{2014-2016}{MSU Denver}{Advisor: Andrew Bonham}
\begin{achievements}
    \item Created software which designs biosensors that adhere to user specifications.
    \item Invented efficient methods for biosensor design and heuristic analysis. \textbf{480x faster} than previous method.
    \item Created a command line interface.
    \item Tools used: \textbf{Python} with the ``multiprocessing" module (for parallelization).
\end{achievements}

%\experience{Undergraduate Summer Intern}{Advisor: Cory Wilson}{Rational Protein Design}{2013, Yale}{Protein Synthesis}

%\begin{achievements}
%    \item Synthesized and characterized ten new designs for E. coli's adenylate kinase enzyme.
%    \item Skills involved: bacterial culture, gene synthesis, plasmid insertion, DNA extraction \& purification, protein extraction \& purification, and enzyme thermal-stability analysis via differential scanning calorimetry. 
%\end{achievements}

%\experience{Undergraduate Researcher and Project Manager}{Advisor: Douglas Petcoff}{Understanding Maturation and Apoptosis in X. Lavis Oocytes}{2011-2013, MSU Denver}{Experimental Cell Biology}

%\begin{achievements}
%    \item Designed and executed experiments aimed at elucidating the roles of sphingolipids and oxidative stress in maturation and apoptosis in Xenopus laevis oocytes. 
%    \item Supervised other undergraduates and ensured our lab had the equipment and materials needed for the project.
%\end{achievements}

%%%%%%%%%%%%%%%%%%%%%
%    Education
%%%%%%%%%%%%%%%%%%%%%
\vspace{-5pt}
\header{Education}
\vspace{-14pt}
\begin{multicols}{2}
    
\school{UC Berkeley}{Computational Biology PhD program}{2016 - 2019}{GPA: 3.7/4.0}

\columnbreak
\schooltwo{MSU Denver}{Theoretical Mathematics}{2011 - 2015}{GPA: 3.9/4.0}{Computer Science, Chemistry}{Summa Cum Laude}

\end{multicols}

\newpage

\contact{\huge{Aviva Bulow}}{\text{aviva.bulow@gmail.com}}{+1(720)473-3836}{github.com/aviva-bulow}{linkedin.com/in/aviva-bulow}

\vspace{-10pt}
\vspace{-10pt}

%%%%%%%%%%%%%%%%%%%%%
%   Projects
%%%%%%%%%%%%%%%%%%%%%

\header{Additional Projects}

\project{Garden Timelapse}
    \begin{achievements}
        \item Set up a Raspberry Pi to take photos of my garden for a time lapse video.
        \item Tools used: Raspberry Pi, Bash, Cron, Motion
    \end{achievements}
    
\project{Wine Tasting Tracker}
    \begin{achievements}
        \item Created a peice of software to track wine and cheese tasting, rating, and pairing.
        \item Tools used: Java
    \end{achievements}
    
\project{Food Journal}
    \begin{achievements}
        \item Wrote a program that tracked what I ate. 
        \item Tools used: Java, Bash
    \end{achievements}
        

%%%%%%%%%%%%%%%%%%%%%
%  Presentations
%%%%%%%%%%%%%%%%%%%%%

\header{Presentations}
\begin{itemize}
    \item Poster presented at UC Berkeley’s Computational Biology student retreat. \href{https://drive.google.com/file/d/1KP7PMcwjiTxELFN4eLtC5HGHk9OF8_WL/view?usp=sharing}{\emph{The Distortion of an Assembly.}} A. Bulow, T. Courtade, 2017.
    
    \item Oral presentation at MSU's undergraduate research conference. \href{https://drive.google.com/open?id=1Qp-pwFFNq9W6Y1yXco7bPYb9gR42gzD2}{\emph{Development of Algorithmic, Graph-Based Techniques for the Automated Design of DNA Biosensors.}} A. Bulow, J. Stephens, A. Bonham, 2015.
    
    \item Poster presented at Yale's undergraduate poster session. \href{https://drive.google.com/open?id=1Nw7wZhaQDygO1d3IZz-vhO8EmXwR53my}{\emph{Conferring Temperature Adapted Function by Rational Protein Design.}} A. Bulow, S. Howell, C. Wilson, 2013.
    
    \item Oral presentation at Yale. \href{https://drive.google.com/open?id=1sF4QX-CQlN3W_EaFlgoVAvbmasgJ1z5q}{\emph{Redesigning E. coli's Adenylate Kinase for Enhanced Thermostability.}} A. Bulow, S. Howell, C. Wilson, 2013.
    
    \item Poster presented at the American Society for Cell Biology. \href{https://drive.google.com/open?id=1Vq4hbrAPjBWLphlA4Se0KVR6hjOEQe-S}{\emph{Sphingolipids Cause Release From Meiotic Arrest and Onset of Apoptosis in Xenopus Oocytes.}} A. Bulow, M. Kunitsyna-	Marev, D. W. Petcoff, 2012.
    
    \item Poster presented at the ASBMB annual meeting. \href{https://drive.google.com/open?id=13EF6xDcyMrBdnJIrP-nvODf55aXsTH6-}{\emph{Sphingolipid Metabolism in Xenopus laevis Oocyte Maturation and Apoptotic Death.}} D. W. Petcoff, A. Bulow, T. D. Hostetter, 2012.
    
    \item Oral presentation at MSU's Undergraduate Research Day conference. \href{https://drive.google.com/open?id=1ln5oxNm-i0YR0fhrTjiymTV8P7ksthtm}{\emph{Life and Death in Xenopus laevis Oocytes.}} A. Bulow, T. H. Hostetter, D. W. Petcoff, 2012.
    
    \item Poster presented at the ASCB annual meeting. \href{https://drive.google.com/open?id=1WiOZdf3LeyTG-4txPeANV7zDjhcjQIQ5}{\emph{The Role of Lipids in Induction of Apoptosis in Xenopus Oocytes.}} D. W. Petcoff, A. Bulow, 2011.
    

\end{itemize}




%%%%%%%%%%%%%%%%
%   Awards
%%%%%%%%%%%%%%%%

\header{Grants, Honors, and Awards}
\begin{itemize}
	\item 2019 \textbf{Travel Grant} to attend the Grad Cohort Workshop for Women
    
   \item 2016 \textbf{Chancellor's Fellowship} for Graduate Study at UC Berkeley (a two year fellowship).
   %\item 2015 \textbf{Summa Cum Laude}, graduation with distinction from MSU Denver.
   \item 2015  \textbf{Achievement Award} for exceptional accomplishments in Theoretical Mathematics, presented by the department of Mathematical and Computer Sciences at MSU Denver
   \item 2013  \textbf{Sackler/NSF REU fellowship} grant to perform research at Yale for a summer.
   \item 2012  \textbf{Undergraduate Research Grant} for \textit{Investigation into the Role of Oxidative Stress on Oocyte Maturation}.
   \item 2012 \textbf{Student Travel Grant} to attend the American Society for Cell Biology annual meeting.
   \item 2012 \textbf{Undergraduate Research Grant} for \textit{Investigation of Apoptosis and Maturation in Xenopus Laevis Oocytes}.
   \item 2012 \textbf{Student Travel Grant} to attend the American Society for Microbiology annual meeting. 
   \item 2011    \textbf{LAS Dean's grant} for research into \textit{Oxidative stress and apoptotic death in Xenopus oocytes}
   \item 2011    \textbf{Goldwater Scholarship} Honorable Mention

\end{itemize}

%%%%%%%%%%%%%%%%
%   Volunteer
%%%%%%%%%%%%%%%%

\header{Volunteer Experience}
\begin{itemize}
    \item 2018	\textbf{Founder} of the Computational Biology student group
    \item 2017/2018 \textbf{Graduate Student Representative} for  Computational Biology
    \item 2017 \textbf{Recruiter} at SACNAS, a diversity in STEM conference.
    \item 2017 \textbf{Coordinator} for the Computational Biology weekly events mailing list.
    \item 2017  \textbf{Member of the planning committee} for the 2017 Computational Biology and Genomics retreat.
    \item 2017 Engaged in the Chancellor's Graduate Student Fireside Chat - Status of Black Graduate Students. (I was one of five students selected to participate.)
    
\end{itemize}

\end{document}
